---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(SPCreporter)
```

This vignette covers how to get started with {SPCreporter}.  We are going to produce an example report using example files that are bundled into this package.  Everything is self-contained.  You'll have your first report in no time!

The example uses three _xlsx_ files which are located in the "example_data" folder of the package.

```{r}
#| eval: false

# set up to read the package files. You will not need to do this to read your own data.
example_files <- system.file("example_data", package="SPCreporter")

####
# 1. READ THE DATA FILES IN
#############################

# read in measure data from the two worksheets in the example file
measure_data <- list(
  week = readxl::read_xlsx(file.path(example_files, "data.xlsx"), sheet = "week"),
  month = readxl::read_xlsx(file.path(example_files, "data.xlsx"), sheet = "month")
)

# read in the report config from example file
report_config <- readxl::read_xlsx(file.path(example_files, "report_config.xlsx"))

# read in measure config from example file
measure_config <- readxl::read_xlsx(file.path(example_files, "measure_config.xlsx"))

####
# 2. CREATE THE DATA BUNDLE
#############################

# create the data bundle
data_bundle <- spcr_make_data_bundle(
  measure_data = measure_data, 
  report_config = report_config,
  measure_config = measure_config 
)

####
# 3. MAKE THE REPORT
#############################

# make the report, including information for the six mandatory arguments.
spcr_make_report(
  data_bundle = data_bundle,
  report_title = "My Example Report",
  report_ref = "EG.001",
  data_cutoff_dttm = as.POSIXct("2022-09-30 23:59:59"),
  author_name = "Anne Author",
  author_email = "a.author@example.com"
)


```

You should now have an example report in your working directory

After running this example, the next stage is to move the example files to your machine, and start to modify them to create a report of your own data.  
