---
title: "Creating multiple reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example - creating multiple reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(SPCreporter)
```

This vignette covers a more advanced example, using {purrr} to map over several versions of the configuration data files, to produce multiple sets of reports.  

You might do this to produce similar reports customised for different business areas with a single command, or to produce tiered sets of reports (low detail, medium detail, full detail) for use at different levels in your business.  

As a simple example the codes below generates 3 example reports with different background colours.  

```{r}
#| eval: false

# example where we map over several reports, creating them in one go

all_my_reports <- tibble::tibble(
  report_title = c("Report 1", "Report 2", "Report 3"),
  report_ref = c("ID.1", "ID.2", "ID.3"),
  author_name = "Anne Author",
  author_email = "a.author@example.com",
  data_cutoff_dttm = as.POSIXct("2022-09-30 23:59:59"),
  # create reports with different paper colours
  paper_colour = c("seashell", "thistle", "#afcfaf")
)

# map over the dataframe, which will create 3 separate reports
# in this case with the same dataset...
purrr::pwalk(all_my_reports, spcr_make_report, data_bundle = data_bundle)

# ... but you may want to pass different data to each:
all_my_reports |>
  dplyr::mutate(data_bundle = list(data_bundle1, data_bundle2, data_bundle3)) |>
  purrr::pwalk(spcr_make_report)

```
